---
title: "Run Club Event & Email Text"
format: html
editor: visual
params: 
  bar_abbr: "Bye & Bye"
execute: 
  echo: false
  warning: false
  error: false
date: today
---

```{r}
#| label: set-up
library(tidyverse)
library(janitor)
library(googlesheets4)

```

```{r}
#| label: authenticate

gs4_auth(email = "em323ily@gmail.com")
```


```{r}
#| label: get-data

venue_url <- "https://docs.google.com/spreadsheets/d/17KIATzL90vfhzBOlO5v5cyIzjT0ewYoFSVEwAAqcqZI/"

venues_raw <- read_sheet(venue_url,
                         sheet = "Venues")

# Create a lookup table of which connector words to use based on the route type
route_words <- tibble("route_type" = c("loop", "out-and-back"),
                      "connector_words" = c("around", "on the"))

```

```{r}
#| label: functions

# Function to get the quadrant name based on the address
get_quadrant_name <- function(address){
  quadrant = case_when(str_detect(address, " SE ") ~ "Southeast",
                       str_detect(address, " NE ") ~ "Northeast",
                       TRUE ~ NA)
  return(quadrant)
}

# Function to get the wording about route
get_route_wording <- function(exception, route_type, connector_words, quadrant, waterfront){
  route_wording = case_when(is.na(exception) == FALSE ~ paste0(route_type, " ", connector_words, " ", exception),
                            waterfront == "No" ~ paste0(route_type, " ", connector_words, " ", quadrant),
                            waterfront == "Yes" ~ paste0(route_type, " ", connector_words, " the waterfront"),
                            TRUE ~ NA)
  return(route_wording)
}


```



```{r}
#| label: clean-data

# Grab the columns we want
venues <- venues_raw |> 
  clean_names() |> 
  select(bar, bar_abbr, address, current_map, route_length, route_type, waterfront, exception, google_link)

# Apply functions and join the route_words dataset
venues_clean <- venues |>
  mutate(quadrant = sapply(address, get_quadrant_name)) |> 
  left_join(route_words, by = "route_type") |> 
  mutate(route_wording = pmap(list(exception, route_type, connector_words, quadrant, waterfront), get_route_wording))

```


```{r}
#| label: parameters

current_venue <- venues_clean |> 
  filter(bar_abbr == params$bar_abbr)

```


# Event Text

Hello Run Chuggers!

Today we'll meet at `{r} current_venue$bar` in `{r} current_venue$quadrant` (`{r} current_venue$address`) for a `{r} current_venue$route_length` mile `{r} current_venue$route_wording`! We will meet around 6:55pm at `{r} current_venue$bar_abbr` and leave for the run at 7:05pm.

Don't forget your I.D! Also, if you have reflective gear or a light to run with, we recommend bringing that too.

Click here for the route: \[UPDATE LINK\] `{r} current_venue$current_map`

If you have any questions, feel free to reach out!

See you all tonight!!

# Email Text

Subject Line: `{r} format(Sys.Date(), "%m/%d")` Run & Chug!

Hello Run Chuggers!

Today we'll meet at `{r} current_venue$bar` in `{r} current_venue$quadrant` (`{r} current_venue$address`) UPDATE `{r} current_venue$google_link` for a `{r} current_venue$route_length` mile `{r} current_venue$route_wording`! We will meet around 6:55pm at `{r} current_venue$bar_abbr` and leave for the run at 7:05pm.

Don't forget your I.D! Also, if you have reflective gear or a light to run with, we recommend bringing that too.

Click here for the route: UPDATE LINK

If you have any questions, feel free to reach out!

See you all tonight!!
